\subsection*{Law of Nested Equilibrium}
\hrule
\vspace{0.3cm}
\GetLaw{LawOfNestedEquilibrium}
\vspace{0.5cm}

\subsubsection*{Conceptual Overview}
This law extends the concept of stability from a single system to a system-of-systems.  It demonstrates a fractal-like nature of stability: a supersystem composed of multiple stable spirals is itself stable if and only if the convergence points of those spirals form a stable configuration according to the Law of Algebraic Stability. 

\subsubsection*{Formal Proof}
The proof connects the \textbf{Law of Invariant Geometric Sum} with the \textbf{Law of Algebraic Stability}. We will show that the condition for the stability of a supersystem of spirals is mathematically identical to the condition for the stability of their initial starting points. 

\begin{enumerate}
    \item Consider a supersystem composed of $N$ spirals. Each individual spiral, $i$, begins at a starting point $p_i$.

    \item According to the \textbf{Law of Invariant Geometric Sum}, each spiral $i$ converges to an equilibrium point $\Sigma_i$, given by the formula:
    $$ \Sigma_i = \frac{p_i}{1 - \LambdaG} $$

    \item The equilibrium point of the entire supersystem, $\Sigma_{\text{total}}$, is the sum of the equilibrium points of the individual spirals:
    $$ \Sigma_{\text{total}} = \sum_{i=1}^{N} \Sigma_i = \sum_{i=1}^{N} \frac{p_i}{1 - \LambdaG} $$
    
    \item Since the term $\frac{1}{1 - \LambdaG}$ is a constant for all spirals, we can factor it out of the summation by the distributive property:
    $$ \Sigma_{\text{total}} = \frac{1}{1 - \LambdaG} \left( \sum_{i=1}^{N} p_i \right) $$

    \item For the supersystem to be in equilibrium, its total convergence point must be zero: $\Sigma_{\text{total}} = 0$.
    
    \item Because we have already proven that $|\LambdaG| < 1$, the denominator $(1 - \LambdaG)$ is a non-zero constant. Therefore, the only way for the equation in step 4 to be true is if the summation of the starting points is zero:
    $$ \sum_{i=1}^{N} p_i = 0 $$

    \item This condition, $\sum p_i = 0$, is the definition of a stable system of points according to the \textbf{Law of Algebraic Stability}. 
\end{enumerate}
Therefore, it is formally **proven** that a supersystem of spirals is stable if and only if its set of initial points constitutes a stable system.

\subsubsection*{Computational Verification}
The following Python script symbolically proves this equivalence. It confirms that the ratio of the general term of the supersystem's stability equation ($\Sigma_i$) to the general term of the starting points' stability equation ($p_i$) is a non-zero constant. This demonstrates that the sum of all $\Sigma_i$ is zero if and only if the sum of all $p_i$ is zero.

\paragraph{Python Verification Script}
\begin{lstlisting}[language=Python, caption={Symbolic script to prove the Law of Nested Equilibrium.}, label={lst:nested_equilibrium_proof}]
import sympy

def prove_nested_equilibrium():
    """
    Symbolically proves the Law of Nested Equilibrium using the robust
    method of asserting the difference between expressions is zero.
    This version disables Unicode output for LaTeX compatibility.
    """
    print("=" * 60)
    print("Final Symbolic Proof of the Law of Nested Equilibrium")
    print("=" * 60)

    # Define symbolic variables
    T, J = sympy.symbols('T J', real=True)
    i = sympy.Symbol('i', integer=True)
    p = sympy.IndexedBase('p')

    # Define the operator
    Lambda_G1 = T + sympy.I * J

    # Define the general terms
    sigma_term = p[i] / (1 - Lambda_G1)
    p_term = p[i]

    # Calculate the ratio of the two general terms
    ratio = sympy.simplify(sigma_term / p_term)

    # Define what the ratio is expected to be
    expected_ratio = 1 / (1 - Lambda_G1)

    print("The script will verify that the ratio of the general terms")
    print("(sigma_term / p_term) is algebraically equal to 1 / (1 - Lambda_G1).")
    print("It does this by confirming their difference simplifies to zero.")

    # Assert that the DIFFERENCE between the two forms is zero. This is the robust test.
    assert sympy.simplify(ratio - expected_ratio) == 0

    print("Since the ratio is a non-zero constant,")
    print("Sum(sigma_term) = 0 if and only if Sum(p_term) = 0.")
    print("Proof Status: PROVEN")
    print("=" * 60)


if __name__ == '__main__':
    prove_nested_equilibrium()
\end{lstlisting}

\paragraph{Verification Output}
\begin{verbatim}
============================================================
Final Symbolic Proof of the Law of Nested Equilibrium
============================================================
The script will verify that the ratio of the general terms
(sigma_term / p_term) is algebraically equal to 1 / (1 - Lambda_G1).
It does this by confirming their difference simplifies to zero.
Since the ratio is a non-zero constant,
Sum(sigma_term) = 0 if and only if Sum(p_term) = 0.
Proof Status: PROVEN
============================================================
\end{verbatim}