\subsection*{Law of Algebraic Stability}
\hrule
\vspace{0.3cm}
\GetLaw{LawOfAlgebraicStability}
\vspace{0.5cm}

\subsubsection*{Conceptual Overview}
This is the foundational principle of equilibrium in the framework. It provides a simple, computable method for determining if a collection of points is in a state of perfect balance. The concept of a zero Center of Gravity is the idealized state that all dynamic systems strive to return to. The drive to achieve this zero-state is the ultimate source of all interaction and motion in the theory.

\subsubsection*{Formal Proof}
The proof relies on formalizing the definition of the "Center of Gravity" (CG) vector for a system of points in the complex plane. The law posits that a system is stable if and only if this vector is zero.

\begin{enumerate}
    \item Let a system be defined by a set of $N$ points $\{p_1, p_2, \dots, p_N\}$ and a corresponding set of harmonic weights $\{w_1, w_2, \dots, w_N\}$, where the weights are chosen from the core constants $\{T, J, K, \dots\}$.

    \item The Center of Gravity vector, $\Xi$, for this system is defined as the weighted sum of the point vectors:
    $$ \Xi = \sum_{i=1}^{N} w_i p_i $$
    For example, for a simple two-body system, this might be $\Xi = T p_1 + J p_2$.

    \item The law defines "stability" as the state where the Center of Gravity vector is zero:
    $$ \Xi = 0 $$
    
    \item This definition serves as the axiom of equilibrium. Later laws, such as the \textbf{Law of Dissonant Propulsion}, equate this $\Xi$ vector (the "Dissonance Vector") directly to the source of motive force. Therefore, a state of $\Xi = 0$ is a state of zero net force, which is the definition of equilibrium.
\end{enumerate}
The law is thus established as the fundamental definition of stability upon which other laws of dynamics are built.

\subsubsection*{Computational Verification}
The following Python script implements a function to calculate the Center of Gravity vector ($\Xi$). It then uses this function to test a simple two-point system that has been explicitly constructed to be stable, verifying that its Center of Gravity is indeed zero.

\paragraph{Python Verification Script}
\begin{lstlisting}[language=Python, caption={Symbolic script to implement and test the Law of Algebraic Stability.}, label={lst:algebraic_stability_proof}]
import sympy


def prove_algebraic_stability():
    """
    Implements and verifies the Law of Algebraic Stability for a
    simple, constructed two-body system. This version uses the
    correct SymPy type for initialization.
    """
    print("=" * 60)
    print("Computational Test of the Law of Algebraic Stability")
    print("=" * 60)

    # Define symbolic constants
    T, J, p1 = sympy.symbols('T J p1')

    # Construct a second point, p2, that is guaranteed to create a
    # stable system with p1 under weights T and J.
    # If T*p1 + J*p2 = 0, then p2 = -(T/J)*p1
    p2 = -(T / J) * p1

    print(f"Constructing a stable two-point system:")
    print(f"p1 = {p1}")
    print(f"p2 = {p2}")

    # Define the points and weights for our test system
    points = [p1, p2]
    weights = [T, J]

    # Calculate the Center of Gravity (Dissonance Vector)
    # Initialize the sum with SymPy's Integer(0) to avoid type errors.
    center_of_gravity = sympy.Integer(0)
    for i in range(len(points)):
        center_of_gravity += points[i] * weights[i]

    center_of_gravity = sympy.simplify(center_of_gravity)

    print(f"Calculated Center of Gravity (Xi = T*p1 + J*p2):")
    print(center_of_gravity)

    # Assert that the Center of Gravity for this stable system is zero
    assert center_of_gravity == 0

    print("Proof Status: VERIFIED")
    print("The constructed stable system has a Center of Gravity of 0.")
    print("=" * 60)


if __name__ == '__main__':
    prove_algebraic_stability()
\end{lstlisting}

\paragraph{Verification Output}
\begin{verbatim}
============================================================
Computational Test of the Law of Algebraic Stability
============================================================
Constructing a stable two-point system:
p1 = p1
p2 = -T*p1/J
Calculated Center of Gravity (Xi = T*p1 + J*p2):
0
Proof Status: VERIFIED
The constructed stable system has a Center of Gravity of 0.
============================================================
\end{verbatim}